%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Working Student \& Backend Engineer} % Job title
    {Camunda Services GmbH.} % Organization
    {Berlin, Germany} % Location
    {Apr. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project page: https://github.com/zeebe-io/}
        \item {Working on configuration management.}
        \item {Command line interface developing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Internship Student} % Job title
    {3YOURMIND GmbH} % Organization
    {Berlin, Germany} % Location
    {Oct. 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhancing 3D-Druck Netzwerk Website https://3d-druck-netzwerk.de/.}
        \item {Organising event for 3D Printing Community.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Technicolr} % Organization
    {Shanghai, China} % Location
    {Nov. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Previously CDBU of Cisco System was sold to Technicolor, the deal started in July 2015 and finished in November 2015.}
        \item {Developing and debugging on HAL layer and Linux system environment. Mainly using C and Linux shell script.}
        \item {2 months' field work in San Francisco, USA with Ericsson for integrating their "Mediaroom" platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Cisco} % Organization
    {Shanghai, China} % Location
    {Jun. 2014 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working in CDBU at Cisco as an Embed System Software Engineer, focusing on developing Hardware Abstract Layer in Set-top Box.}
        \item {One of the main developers in 4K set-top box project, based on Linux shell script and C language.}
        \item {Implemented Embedded Diagnostic System on set-top box, based on DirectFB and C++.}
        \item {Be responsible for maintaining Windows CE set-top box, made some utilities for those boxes and got good feedback from manager.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Front-end Internship} % Job title
  %   {Playcrab Inc.} % Organization
  %   {Beijing, China} % Location
  %   {Nov. 2013 - Mar. 2014} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Implemented UI of Games based on cocos2d-x, within Lua Programming language.}
  %       \item {Modified some picture of the Game, by Photoshop}
  %     \end{cvitems}
  %   }



%---------------------------------------------------------
\end{cventries}
